A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-16 EvoPar2017/paper.Rnw
Adds package
Adds @mariosky's algorithm
And this is the final one.
Closes #131
Closes #132
Closes #127
Fixed typos
and while we're at it, closes #132, closes #127

\usepackage[latin1]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{url}
\usepackage{caption}

@@

In this section we present {\sf NodIO}, a distributed volunteer-based 
evolutionary computation system immplemented in JavaScript. 
All parts of the framework are free and available
with a free license from \url{https://ANONYMOUS-URL}.
%\url{https://github.com/JJ/splash-volunteer}.

The architecture of the {\sf NodIO} system is divided in two tiers:
\begin{enumerate}
\item A REST (representational state transfer) server that responds to
  HTTP requests made by the browsers. These HTTP requests use JSON for information 
  encoding, in this case chromosomes and related
  information sent by the clients, and responses returned by the
  server.  The server has the capability to
  run a single experiment, storing the incoming chromosomes in a
  key-value cache that uses as key the chromosome string itself and is
  reset when the solution is found. This cache has a finite 
  size that erases the oldest chromosomes once it has been filled to % Also "it has been filled to its"
  its maximum capacity.  
\item A client that includes the evolutionary algorithm as
  JavaScript code embedded in a web page that displays the fitness and
  other graphs, some
  additional links, and information on the experiment. 
  This code runs
  an evolutionary algorithm {\em island} that starts with a random
  population, then after every 100 generations, it sends the best individual
  back to the server (via a {\tt PUT} request), and then requests a random
  individual back from the server (via a {\tt GET} request). We have
  kept the number of generations between migrations fixed since it is
  a way of finding out how much real work every client is doing. In
  the version of the server used in this paper, we implemented a
  policy by which the combination IP-fitness chromosome could only be
  inserted once into the cache. That means that if a particular IP
  sends a fitness value of 99 into the server, it will be accepted only
  once. The main intention of this policy was to avoid {\em
    overlapping} of contributions, with clients still running an {\em
    old} run of the experiment contributing after a new one had
  started. This however did not completely avoid these contributions: if the
  clients of the {\em old} run increased their new fitness, it would
  still be allowed. 
\end{enumerate}

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different JavaScript libraries, such as JQuery or {\tt
  Chart.js} have been used to build the user interface elements of the
framework, which should be running in \url{http://ANONYMOUS-URL}, 
%\url{http://nodio-jmerelo.rhcloud.com}, 
a free resource hosted in the
OpenShift Platform as a Service\footnote{It is not guaranteed to be running,
or running the same version, when you read this, however; you can always get
the sources from GitHub and set it up yourself.}.
%
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{system.pdf}
\caption{Description of the NodIO system. Clients execute a JavaScript EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one back from the server.}
\label{fig:system}
\end{figure}

>>>>

\usepackage[latin1]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{url}
\usepackage{caption}
\usepackage{algorithm,algorithmic}

@@

In this section we present {\sf NodIO}, a distributed volunteer-based 
evolutionary computation system implemented in JavaScript. 
All parts of the framework are free and available
with a free license from \url{https://ANONYMOUS-URL}.
%\url{https://github.com/JJ/splash-volunteer}.

The architecture of the {\sf NodIO} system is divided in two tiers:
\begin{enumerate}
\item A REST (representational state transfer) server that responds to
  HTTP requests made by the browsers. These HTTP requests use JSON for information 
  encoding, in this case chromosomes and related
  information sent by the clients, and responses returned by the
  server.  The server has the capability to
  run a single experiment, storing the incoming chromosomes in a
  key-value cache that uses as key the chromosome string itself and is
  reset when the solution is found. This cache has a finite 
  size that erases the oldest chromosomes once it has been filled to % Also "it has been filled to its"
  its maximum capacity.  
\item A client that includes the evolutionary algorithm as
  JavaScript code embedded in a web page that displays the fitness and
  other graphs, some
  additional links, and information on the experiment. 
  This code runs
  an evolutionary algorithm {\em island} that starts with a random
  population, then after every 100 generations, it sends the best individual
  back to the server (via a {\tt PUT} request), and then requests a random
  individual back from the server (via a {\tt GET} request). We have
  kept the number of generations between migrations fixed since it is
  a way of finding out how much real work every client is doing. In
  the version of the server used in this paper, we implemented a
  policy by which the combination IP-fitness chromosome could only be
  inserted once into the cache. That means that if a particular IP
  sends a fitness value of 99 into the server, it will be accepted only
  once. The main intention of this policy was to avoid {\em
    overlapping} of contributions, with clients still running an {\em
    old} run of the experiment contributing after a new one had
  started. This however did not completely avoid these contributions: if the
  clients of the {\em old} run increased their new fitness, it would
  still be allowed. 
\end{enumerate}
%
\begin{algorithm}
\caption{Algorithm for each of the clients in a web browser.\label{algorithm}}
\begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\REQUIRE $ea$, $period$, $population\_size$
\ENSURE $best$
\\ 
\textit{Initialization} :
\STATE create a random population of $ea.population.size$ =
$population\_size$
\STATE generation\_count = 0
\\ 
\textit{EA LOOP:}
\WHILE{$(ea.population.best \ne best\_fitness)$}
\STATE $ea.generation()$
\STATE $generation\_count++$
\IF {$((generation\_count \bmod period) == 0)$}
\STATE \texttt{GET} $random$
\STATE ea.population.add(random)
\STATE \texttt{PUT} ea.population.best
\STATE \texttt{GET} statistics
\STATE update GUI with statistics
\ENDIF
\ENDWHILE
\RETURN $ea.population.best$
\end{algorithmic}
\end{algorithm}

Figure \ref{fig:system} describes the general system architecture; the 
algorithm is described in \ref{algorithm}. Different JavaScript libraries, such as JQuery or {\tt
  Chart.js} have been used to build the user interface elements of the
framework, which should be running in \url{http://ANONYMOUS-URL}, 
%\url{http://nodio-jmerelo.rhcloud.com}, 
a free resource hosted in the
OpenShift Platform as a Service\footnote{It is not guaranteed to be running,
or running the same version, when you read this, however; you can always get
the sources from GitHub and set it up yourself.}.
%
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{system.pdf}
\caption{Description of the NodIO system. Clients execute a JavaScript EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one back from the server.}
\label{fig:system}
\end{figure}
